---
title: "Newmark Analytics - BRAND REPUTATION DETERMINANTS"
author: "Elizabeth Josephine"
date: "23/03/2021"
output: github_document
---

# PROBLEM DEFINITION
## **a) Specifying the Question**

Assessing factors that contribute to the brand reputation in Kenya from the consumer's perspective. 

## **b) Defining the metrics for success**

Unsupervised learning ML algorithms

## **c) Understanding the context**

Newmark Analytics is carrying out survey entitled: "Determinants of brand reputation perception among consumers in Kenya." The purpose of this research is to assess factors that contribute to brand reputation in Kenya from the customer's perspective.

## **d) Recording the Experimental Design**

1. Define the question, the metric for success, the context, experimental design taken.
2. Read and explore the given dataset.
3. Find and deal with outliers, anomalies, and missing data within the dataset.
4. Perform Exploratory Data Analysis
 
## **e) Relevance of the data**

The data used for this project will inform the PR department on the factors that contribute to brand reputation in Kenya from the customer's perspective.

# DATA ANALYSIS
## DATA SOURCING
```{R}
# loading libraries
library(relaimpo)
library(data.table)
library(ggplot2) # Data visualization
library(ggthemes) # Plot themes
library(plotly) # Interactive data visualizations
library(dplyr) # Data manipulation
library(psych) # Will be used for correlation visualization
```


```{R}
# importing our data
# reading our data

library(readxl)
df <- read_excel("D:/submissions.xlsx")
df
```

## DATA CHECKING
```{R}
# previewing the dataset
View(df)

```

```{R}
# previewing the column names
colnames(df)

```

```{R}
# previewing the dataset
class(df)

```

```{R}
# previewing the datatypes of the dataset
sapply(df, class)
```

```{R}
# previewing the head of the dataset
head(df, n = 5)

```

```{R}
# previewing the tail of the dataset
tail(df, n = 5)

```

```{R}
# checking the structure of the data
str(df)

```

```{R}
# checking the dimension/shape of the data
dim(df) # 167 rows and 112 columns
```
## DATA CLEANING
### Missing Values
``` {r}
# checking for missing values
sum(is.na(df))# there are 3765 missing values in the data
```

```{R}
#deleting columns with missing values
df1 <- df[ , colSums(is.na(df)) == 0]
sum(is.na(df1))
```

### Duplicates

``` {r}
# checking for duplicates
duplicated_rows <- df1[duplicated(df1),]
duplicated_rows # there are no duplicates in the data
```

``` {r}
# showing these unique items and assigning to a variable unique_items below
unique_items <- df1[!duplicated(df1), ]
unique_items
```

```{R}
#viewing the remaining columns
colnames(df1)
```

```{R}
View(df1)
```

```{r}
# selecting the numerical data columns
df2 <- df1 %>% select_if(is.numeric)
df2
```

```{R}
# visualizing any outliers in the data
par (mfrow= c ( 3, 3))
for (i in 1 : length (df2)) {
boxplot (df2[,i], main= names (df2[i]), type= "l" )
}
```
# EXPLORATORY DATA ANALYSIS
## FEATURE ENGINEERING
```{R}
View(df2)
```

```{R}
# selecting the required columns for analysis 
# since there are several brands in the questionnaire, i will use the fast moving consumer goods as a sample for the whole data on section D to determine the factors that play a keyrole in the reputation of a brand
# selecting the required columns for analysis in fast moving consumer goods
df3 <- subset(df2, select = c("REPUTATION-Q1", "REPUTATION-Q2", "REPUTATION-Q4", "REPUTATION-Q6", "REPUTATION-Q7", "REPUTATION-Q8", "REPUTATION-Q10", "REPUTATION-FMCGOFF2", "REPUTATION-FMCGOFF3", "REPUTATION-FMCGINNO2",  "REPUTATION-FMCGRFS1",  "REPUTATION-FMCGSA1", "REPUTATION-FMCGTR1", "REPUTATION-FMCGOP1"))
# renaming columns for easy analysis
df3 <- df3 %>% rename(monthy_expenditure = "REPUTATION-Q1")
df3 <- df3 %>% rename(purchase_consideration = "REPUTATION-Q2")
df3 <- df3 %>% rename(price_variations = "REPUTATION-Q4")
df3 <- df3 %>% rename(gender = "REPUTATION-Q6")
df3 <- df3 %>% rename(education_level = "REPUTATION-Q7")
df3 <- df3 %>% rename(age_bracket = "REPUTATION-Q8")
df3 <- df3 %>% rename(conversance = "REPUTATION-Q10")
df3 <- df3 %>% rename(informative = "REPUTATION-FMCGOFF2")
df3 <- df3 %>% rename(problem_solving = "REPUTATION-FMCGOFF3")
df3 <- df3 %>% rename(pioneering_products = "REPUTATION-FMCGINNO2")
df3 <- df3 %>% rename(appealing_m_campaign = "REPUTATION-FMCGRFS1")
df3 <- df3 %>% rename(satisfaction = "REPUTATION-FMCGSA1")
df3 <- df3 %>% rename(trustworthy = "REPUTATION-FMCGTR1")
df3 <- df3 %>% rename(honest_straightforward = "REPUTATION-FMCGOP1")
```

```{R}
# previewing the new dataset
View(df3)
```


## UNIVARITE ANALYSIS
### measures of central tendencies and percentiles

``` {r}
# descriptive statistics
# these summaries will provide us with the measures of central tendencies of the numerical columns
summary(df3)
```

### Measures of Disprersion and all other descriptives
```{R}
#descriptive statistics of the numerical columns i.e. all statistics except for the quantile ranges which have been shown in the above summary statistics
describe(df3)
```

### Univariate Graphical
```{R}
df3 <- as.data.frame(sapply(df3, as.numeric))
for (col in 1:ncol(df3[, 1:14])){
  hist(df3[,col], main = names(df3[col]), col = 'lightblue', xlab = names(df3[col]))
}
```

## BIVARIATE ANALYSIS
### covariance
``` {R}
# covariance of variables in section a to section d
cov <- cov(df3)
round(cov, 2)
```

### correlation
``` {R}
coo <- cor(df3)
round(coo, 2)
```
